What Can Stack Traces Tell us about of the use Exceptions in Java?

### 2014-07-11 android-stacks.tex

@@

Although exception handling mechanism has been embedded in several programming languages 
as show above,   the exception handling code is often generally poorly understood and the least
tested part of software systems.

@@

The Java specification~\cite{gosling2000java} suggests that user-defined
exceptions should be checked exceptions. The main reason is because doing so the
callers of a method will know about the exceptions that a method can throw, and
so they can decide what to do about them. However, there is a long-lasting
debate about the use of checked and unchecked exceptions in
Java~\cite{javatut,stackoverlow,debate},\footnote{152 questions in Stackoverlow
are related to this debate} since there are pros and cons associated to each of
them.

Hence, in Java an exception can be thrown in one of the following
circumstances~\cite{gosling2000java}: (i) explicitly thrown when a throw statement is executed; 
(ii) implicitly thrown by the JVM when the evaluation of an expression
 violates the normal semantics of language (e.g., out-of-bounds array index,
division-by-zero, access to a null reference); or (iii) implicitly thrown by
the JVM due to an internal error or resource limitation (e.g.,
OutofMemoryError).

>>>>

Although exception handling mechanism has been embedded in several programming languages 
as show above,   the exception handling code is often generally poorly understood and the least
tested part of software systems. There is a long-lasting debate about the pros and cons of checked and unchecked exceptions 
~\cite{javatut,stackoverlow,debate},\footnote{152 questions in Stackoverlow
are related to this debate}. The debates, however, are based on the developers own experience in
using both models. There is a lack of empirical study tackling the pros and cons of each model.

@@

@@

The Java specification~\cite{gosling2000java} suggests that user-defined
exceptions should be checked exceptions. The main reason is because doing so the
callers of a method will know about the exceptions that a method can throw, and
so they can decide what to do about them.

In Java an exception can be thrown in one of the following
circumstances~\cite{gosling2000java}: (i) explicitly thrown when a throw statement is executed; 
(ii) implicitly thrown by the JVM when the evaluation of an expression
 violates the normal semantics of language (e.g., out-of-bounds array index,
division-by-zero, access to a null reference); or (iii) implicitly thrown by
the JVM due to an internal error or resource limitation (e.g.,
OutofMemoryError).
